First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-06-13 ms.tex
Fixed small typesetting bug in abstract

\begin{abstract}
The Murchison Widefield Array (MWA) has collected hundreds of hours of Epoch of 
Reionization (EoR) data and now faces the challenge of overcoming foreground and 
systematic contamination to reduce the data to a cosmological measurement. We introduce 
several novel analysis techniques such as cable reflection calibration, high resolution 
gridding kernels, diffuse foreground model subtraction, and quality control methods. Each 
change to the analysis pipeline is tested against a two dimensional power spectrum figure 
of merit to demonstrate improvement. We incorporate the new techniques into a deep 
integration of 32 hours of MWA data. This data set is used to place a systematic-limited 
upper limit on the cosmological power spectrum of $\Delta^2 \leq 2.7 \times 10^4$ mK
$^2$ at $k=0.27$ h~Mpc$^{-1}$ and $z=7.1$, consistent with other published limits, and a 
modest improvement (factor of 1.4) over previous MWA results. While our result is 
systematic limited, we identify several strategies to overcome these systematics in future 
analysis.
\end{abstract}
\keywords{cosmology: observations - cosmology: reionization}
\maketitle

>>>>

\begin{abstract}
The Murchison Widefield Array (MWA) has collected hundreds of hours of Epoch of 
Reionization (EoR) data and now faces the challenge of overcoming foreground and 
systematic contamination to reduce the data to a cosmological measurement. We introduce 
several novel analysis techniques such as cable reflection calibration, high resolution 
gridding kernels, diffuse foreground model subtraction, and quality control methods. Each 
change to the analysis pipeline is tested against a two dimensional power spectrum figure 
of merit to demonstrate improvement. We incorporate the new techniques into a deep 
integration of 32 hours of MWA data. This data set is used to place a systematic-limited 
upper limit on the cosmological power spectrum of $\Delta^2 \leq 2.7 \times 10^4$ 
mK$^2$ at $k=0.27$ h~Mpc$^{-1}$ and $z=7.1$, consistent with other published limits, and a 
modest improvement (factor of 1.4) over previous MWA results. While our result is 
systematic limited, we identify several strategies to overcome these systematics in future 
analysis.
\end{abstract}
\keywords{cosmology: observations - cosmology: reionization}
\maketitle
